---
title: "Mortality EP workflow audit"
subtitle: "Companion analysis for `Mortality EP.Rmd`"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-tools: true
execute:
  echo: true
  warning: false
  message: false
  freeze: auto
---

## Scope and intent

This companion document audits the workflow in `Mortality EP.Rmd` without editing the source file.  
Goals:

1. preserve the same mortality endpoint framing (CSP vs BVP),
2. make Bayesian assumptions explicit,
3. use clinically grounded priors on pooled log-OR (`mu`),
4. evaluate prior sensitivity,
5. add posterior predictive checks (PPC),
6. report uncertainty-calibrated interpretation language, and
7. cross-check the core random-effects result with a `brms` front-end using `cmdstanr`.

## Setup and package checks

```{r}
# Core stack used in this audit
core_pkgs <- c(
  "bayesmeta",
  "metafor",
  "dplyr",
  "tibble",
  "tidyr",
  "purrr",
  "ggplot2",
  "knitr"
)

missing_core <- core_pkgs[!vapply(core_pkgs, requireNamespace, logical(1), quietly = TRUE)]
analysis_ok <- length(missing_core) == 0

if (analysis_ok) {
  invisible(lapply(core_pkgs, library, character.only = TRUE))
  set.seed(20260418)
  theme_set(theme_minimal(base_size = 12))
} else {
  cat(
    "Core packages missing:", paste(missing_core, collapse = ", "),
    "\nSections requiring these packages are skipped."
  )
}

turner_ok <- requireNamespace("BayesianPriorsTool", quietly = TRUE)
brms_ok <- requireNamespace("brms", quietly = TRUE) && requireNamespace("cmdstanr", quietly = TRUE)

cmdstan_available <- FALSE
if (brms_ok) {
  cmdstan_available <- tryCatch({
    p <- cmdstanr::cmdstan_path()
    !is.null(p) && nzchar(p)
  }, error = function(e) FALSE)
}
```

## Data reconstruction and effect-size derivation

```{r, eval=analysis_ok}
# Reconstructed from Mortality EP.Rmd
mor_data <- tibble::tibble(
  study = c(
    "Vinther, 2021 (HBP)",
    "Wang, 2022 (LBAP)",
    "Huang, 2022 (HBP)",
    "Pujol-Lopez, 2022 (LBAP)",
    "Vijayaraman, 2023 (LBAP)",
    "PhysioSync-HF, 2026 (LBAP)"
  ),
  subgroup = c("HBP", "LBAP", "HBP", "LBAP", "LBAP", "LBAP"),
  ai = c(0, 0, 1, 0, 2, 11),  # CSP events
  n1 = c(25, 20, 25, 35, 50, 87),
  ci = c(0, 0, 4, 2, 2, 4),   # BVP events
  n2 = c(25, 20, 25, 35, 50, 86)
)

# Log-OR and its sampling variance via metafor::escalc.
# add=0.5, to="only0": continuity correction only where needed for zero-event cells.
mor_es <- metafor::escalc(
  measure = "OR",
  ai = ai, n1i = n1,
  ci = ci, n2i = n2,
  data = mor_data,
  slab = study,
  add = 0.5,
  to = "only0"
) |>
  as.data.frame() |>
  dplyr::mutate(sei = sqrt(vi))

knitr::kable(
  mor_es |>
    dplyr::select(study, ai, n1, ci, n2, yi, sei) |>
    dplyr::mutate(
      yi = round(yi, 3),
      sei = round(sei, 3)
    ),
  caption = "Study-level mortality effects (log-OR scale)."
)
```

## Audit notes on the original workflow

1. The original analysis uses an appropriate random-effects Bayesian synthesis (`bayesmeta`) for sparse-event data.
2. Multiple studies have zero events in one or both arms; this can heavily influence log-OR approximation via continuity corrections.
3. The normal-normal hierarchy is practical for transparent Bayesian synthesis, but approximation error can rise with very sparse binary outcomes.
4. A companion analysis should therefore stress-test priors, inspect posterior predictive behavior, and calibrate interpretation to probability magnitudes rather than dichotomous claims.

## Clinically grounded priors for pooled log-OR (`mu`)

The pooled effect is on the log-OR scale (`mu`).  
Clinical intuition for pacing strategy comparisons generally expects modest mortality shifts, not extreme (>2x) effects across broad HF populations. We therefore define a prior set spanning skeptical to mildly CSP-favoring beliefs.

```{r, eval=analysis_ok}
mu_priors <- tibble::tribble(
  ~prior_id, ~clinical_label, ~mu_mean, ~mu_sd,
  "skeptical", "Skeptical/no large mortality shift expected", 0.00, 0.20,
  "weakly_informative", "Allows moderate benefit/harm while ruling out implausible extremes", 0.00, 0.35,
  "mild_csp_favoring", "Mild pre-trial expectation for CSP benefit", log(0.90), 0.30
) |>
  dplyr::mutate(
    prior_or_median = exp(mu_mean),
    prior_or_low95 = exp(mu_mean - 1.96 * mu_sd),
    prior_or_high95 = exp(mu_mean + 1.96 * mu_sd)
  )

knitr::kable(
  mu_priors |>
    dplyr::transmute(
      prior_id,
      clinical_label,
      mu_mean = round(mu_mean, 3),
      mu_sd = round(mu_sd, 3),
      prior_or_median = round(prior_or_median, 3),
      prior_or_low95 = round(prior_or_low95, 3),
      prior_or_high95 = round(prior_or_high95, 3)
    ),
  caption = "Clinically grounded priors for pooled log-OR."
)
```

## Heterogeneity prior (`tau`) and rationale

```{r, eval=analysis_ok}
tau_prior_label <- NULL
tau_prior_fun <- NULL

if (turner_ok) {
  turner_prior <- BayesianPriorsTool::TurnerEtAlPrior(
    outcome = "all-cause mortality",
    comparator1 = "non-pharmacological",
    comparator2 = "non-pharmacological"
  )
  tau_prior_fun <- turner_prior$dprior
  tau_prior_label <- "Turner et al. empiric log-normal heterogeneity prior"
} else {
  # Conservative fallback if BayesianPriorsTool is unavailable.
  tau_prior_fun <- function(x) bayesmeta::dhalfnormal(x, scale = 0.5)
  tau_prior_label <- "Fallback half-normal prior: tau ~ half-normal(0, 0.5)"
}

cat("Tau prior used:", tau_prior_label)
```

## Reference bayesmeta model (normal-normal hierarchy)

```{r, eval=analysis_ok}
fit_bayesmeta <- function(mu_mean, mu_sd, tau_prior) {
  bayesmeta::bayesmeta(
    y = mor_es$yi,
    sigma = mor_es$sei,
    labels = mor_es$study,
    mu.prior.mean = mu_mean,
    mu.prior.sd = mu_sd,
    tau.prior = tau_prior
  )
}

extract_draws <- function(fit, n = 20000) {
  d <- as.data.frame(fit$rposterior(n = n, tau.sample = TRUE))
  # Defensive naming for compatibility across bayesmeta versions
  if (!("mu" %in% names(d)) && ncol(d) >= 1) names(d)[1] <- "mu"
  if (!("tau" %in% names(d)) && ncol(d) >= 2) names(d)[2] <- "tau"
  d
}

ref_prior <- mu_priors |>
  dplyr::filter(prior_id == "weakly_informative")

ref_fit <- fit_bayesmeta(
  mu_mean = ref_prior$mu_mean,
  mu_sd = ref_prior$mu_sd,
  tau_prior = tau_prior_fun
)

ref_draws <- extract_draws(ref_fit)

ref_summary <- tibble::tibble(
  metric = c("mu (log-OR)", "OR", "tau"),
  mean = c(
    ref_fit$summary["mean", "mu"],
    exp(ref_fit$summary["mean", "mu"]),
    ref_fit$summary["mean", "tau"]
  ),
  low95 = c(
    ref_fit$summary["95% lower", "mu"],
    exp(ref_fit$summary["95% lower", "mu"]),
    ref_fit$summary["95% lower", "tau"]
  ),
  high95 = c(
    ref_fit$summary["95% upper", "mu"],
    exp(ref_fit$summary["95% upper", "mu"]),
    ref_fit$summary["95% upper", "tau"]
  ),
  prob_csp_benefit = c(
    mean(ref_draws$mu < 0),
    mean(exp(ref_draws$mu) < 1),
    NA_real_
  )
)

knitr::kable(
  ref_summary |>
    dplyr::mutate(
      dplyr::across(c(mean, low95, high95, prob_csp_benefit), ~ round(.x, 3))
    ),
  caption = "Reference posterior summary (weakly informative mu prior)."
)
```

## Explicit assumptions and limitations of the bayesmeta normal-normal approximation

The model can be written as:

- sampling model: \(y_i \mid \theta_i \sim \mathcal{N}(\theta_i, s_i^2)\),
- random effects: \(\theta_i \mid \mu, \tau \sim \mathcal{N}(\mu, \tau^2)\).

Key assumptions and practical limitations in this mortality setting:

1. **Approximate normality of log-OR estimates**: with sparse events and zero cells, asymptotic normality may be imperfect.
2. **Within-study SE treated as known**: uncertainty in `sei` estimation is not propagated.
3. **Exchangeability**: studies are assumed conditionally exchangeable around one latent mean `mu`.
4. **Continuity-correction dependence**: zero-cell handling can materially alter `yi` and `sei`.
5. **Small-\(k\) fragility**: with only six studies, posterior inferences are sensitive to prior choices for `mu` and especially `tau`.
6. **Marginal (study-level) estimand**: trial-level aggregate OR can obscure patient-level treatment effect heterogeneity.

## Prior sensitivity analysis

```{r, eval=analysis_ok}
sensitivity_tbl <- mu_priors |>
  dplyr::mutate(
    fit = purrr::map2(mu_mean, mu_sd, ~ fit_bayesmeta(.x, .y, tau_prior_fun)),
    draws = purrr::map(fit, extract_draws),
    post_mu_mean = purrr::map_dbl(fit, ~ .x$summary["mean", "mu"]),
    post_mu_low95 = purrr::map_dbl(fit, ~ .x$summary["95% lower", "mu"]),
    post_mu_high95 = purrr::map_dbl(fit, ~ .x$summary["95% upper", "mu"]),
    post_or_mean = exp(post_mu_mean),
    post_or_low95 = exp(post_mu_low95),
    post_or_high95 = exp(post_mu_high95),
    pr_or_lt_1 = purrr::map_dbl(draws, ~ mean(exp(.x$mu) < 1)),
    pr_or_lt_0_9 = purrr::map_dbl(draws, ~ mean(exp(.x$mu) < 0.9)),
    pr_or_gt_1_1 = purrr::map_dbl(draws, ~ mean(exp(.x$mu) > 1.1))
  ) |>
  dplyr::select(
    prior_id, clinical_label,
    post_or_mean, post_or_low95, post_or_high95,
    pr_or_lt_1, pr_or_lt_0_9, pr_or_gt_1_1
  )

knitr::kable(
  sensitivity_tbl |>
    dplyr::mutate(
      dplyr::across(
        c(post_or_mean, post_or_low95, post_or_high95, pr_or_lt_1, pr_or_lt_0_9, pr_or_gt_1_1),
        ~ round(.x, 3)
      )
    ),
  caption = "Posterior sensitivity to alternative clinically grounded mu priors."
)
```

```{r, eval=analysis_ok}
ggplot(
  sensitivity_tbl,
  aes(y = prior_id, x = post_or_mean, xmin = post_or_low95, xmax = post_or_high95)
) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray40") +
  geom_errorbarh(height = 0.15, linewidth = 0.8, color = "#2b6cb0") +
  geom_point(size = 2.5, color = "#2b6cb0") +
  labs(
    title = "Prior sensitivity of pooled mortality OR",
    x = "Posterior pooled OR (95% CrI)",
    y = "mu prior specification"
  )
```

## Posterior predictive checks (PPC)

```{r, eval=analysis_ok}
# Draw posterior predictive replicated effects:
# theta_i^rep ~ N(mu, tau^2), y_i^rep ~ N(theta_i^rep, sei_i^2)
draw_idx <- sample.int(n = nrow(ref_draws), size = 3000, replace = TRUE)
mu_s <- ref_draws$mu[draw_idx]
tau_s <- pmax(ref_draws$tau[draw_idx], 0)

yrep_mat <- vapply(
  X = seq_along(mu_s),
  FUN = function(j) {
    theta_rep <- rnorm(n = nrow(mor_es), mean = mu_s[j], sd = tau_s[j])
    rnorm(n = nrow(mor_es), mean = theta_rep, sd = mor_es$sei)
  },
  FUN.VALUE = numeric(nrow(mor_es))
)

obs_mean <- mean(mor_es$yi)
obs_sd <- stats::sd(mor_es$yi)
rep_mean <- colMeans(yrep_mat)
rep_sd <- apply(yrep_mat, 2, stats::sd)

ppc_stats <- tibble::tibble(
  discrepancy = c("Mean(log-OR)", "SD(log-OR)"),
  observed = c(obs_mean, obs_sd),
  ppc_p_value = c(mean(rep_mean >= obs_mean), mean(rep_sd >= obs_sd))
)

knitr::kable(
  ppc_stats |> dplyr::mutate(dplyr::across(c(observed, ppc_p_value), ~ round(.x, 3))),
  caption = "Posterior predictive discrepancy checks (Bayesian p-values near 0.5 are reassuring)."
)
```

```{r, eval=analysis_ok}
ppc_by_study <- tibble::tibble(
  study = mor_es$study,
  observed = mor_es$yi,
  pred_low95 = apply(yrep_mat, 1, stats::quantile, probs = 0.025),
  pred_med = apply(yrep_mat, 1, stats::quantile, probs = 0.5),
  pred_high95 = apply(yrep_mat, 1, stats::quantile, probs = 0.975)
)

ggplot(ppc_by_study, aes(y = reorder(study, observed))) +
  geom_segment(
    aes(x = pred_low95, xend = pred_high95, yend = reorder(study, observed)),
    linewidth = 1.0,
    color = "gray65"
  ) +
  geom_point(aes(x = pred_med), color = "#2b6cb0", size = 2) +
  geom_point(aes(x = observed), color = "#c53030", size = 2.2) +
  labs(
    title = "Study-level PPC intervals for observed log-OR",
    subtitle = "Red = observed; blue = posterior predictive median; gray = 95% predictive interval",
    x = "log-OR",
    y = NULL
  )
```

## Uncertainty-calibrated interpretation language

```{r, eval=analysis_ok}
calibrated_language <- function(probability) {
  dplyr::case_when(
    probability < 0.55 ~ "no directional evidence",
    probability < 0.75 ~ "weak directional signal",
    probability < 0.90 ~ "moderate directional evidence",
    probability < 0.975 ~ "strong directional evidence",
    TRUE ~ "very strong directional evidence"
  )
}

p_benefit <- mean(exp(ref_draws$mu) < 1)
p_meaningful <- mean(exp(ref_draws$mu) < 0.90)   # >=10% relative reduction threshold
p_harm <- mean(exp(ref_draws$mu) > 1.10)         # >=10% relative increase threshold

interpretation_tbl <- tibble::tibble(
  quantity = c(
    "Pr(OR < 1) for CSP vs BVP",
    "Pr(OR < 0.90): at least 10% relative mortality reduction",
    "Pr(OR > 1.10): at least 10% relative mortality increase"
  ),
  probability = c(p_benefit, p_meaningful, p_harm),
  calibrated_language = c(
    calibrated_language(p_benefit),
    calibrated_language(p_meaningful),
    calibrated_language(p_harm)
  )
)

knitr::kable(
  interpretation_tbl |> dplyr::mutate(probability = round(probability, 3)),
  caption = "Interpretation uses probability-calibrated language rather than binary significance labels."
)
```

Recommended phrasing template for results sections:

- “The posterior probability that CSP reduces mortality versus BVP was `r if (analysis_ok) sprintf('%.1f%%', 100 * p_benefit) else 'NA'`, representing **`r if (analysis_ok) calibrated_language(p_benefit) else 'NA'`**.”
- “For a clinically meaningful threshold (OR < 0.90), posterior probability was `r if (analysis_ok) sprintf('%.1f%%', 100 * p_meaningful) else 'NA'`; this should be interpreted as probability-weighted evidence, not proof of superiority.”

## `brms` front-end with `cmdstanr` backend cross-check

This section verifies whether a Bayesian hierarchical Gaussian meta-analysis fitted in `brms` yields a similar pooled signal and heterogeneity profile.

```{r}
if (!analysis_ok) {
  cat("Cross-check skipped because core analysis packages are unavailable.")
} else if (!brms_ok) {
  cat("Cross-check skipped: `brms` and/or `cmdstanr` not installed.")
} else if (!cmdstan_available) {
  cat("Cross-check skipped: cmdstan toolchain not configured for `cmdstanr`.")
}
```

```{r, eval=analysis_ok && brms_ok && cmdstan_available}
options(mc.cores = max(1, parallel::detectCores() - 1))

brms_df <- mor_es |>
  dplyr::transmute(
    study = factor(study),
    yi = yi,
    sei = sei
  )

# Priors chosen to approximately align with the reference bayesmeta model.
brms_priors <- c(
  brms::prior(
    normal(ref_prior$mu_mean, ref_prior$mu_sd),
    class = "Intercept"
  ),
  brms::prior(normal(0, 0.5), class = "sd")
)

brms_fit <- brms::brm(
  formula = yi | se(sei, sigma = TRUE) ~ 1 + (1 | study),
  data = brms_df,
  family = gaussian(),
  prior = brms_priors,
  backend = "cmdstanr",
  chains = 4,
  iter = 3000,
  warmup = 1500,
  seed = 20260418,
  refresh = 0
)

brms_draws <- posterior::as_draws_df(brms_fit)

compare_tbl <- tibble::tibble(
  engine = c("bayesmeta", "brms+cmdstanr"),
  mu_mean = c(mean(ref_draws$mu), mean(brms_draws$b_Intercept)),
  mu_low95 = c(quantile(ref_draws$mu, 0.025), quantile(brms_draws$b_Intercept, 0.025)),
  mu_high95 = c(quantile(ref_draws$mu, 0.975), quantile(brms_draws$b_Intercept, 0.975)),
  tau_mean = c(mean(ref_draws$tau), mean(brms_draws$sd_study__Intercept)),
  tau_low95 = c(quantile(ref_draws$tau, 0.025), quantile(brms_draws$sd_study__Intercept, 0.025)),
  tau_high95 = c(quantile(ref_draws$tau, 0.975), quantile(brms_draws$sd_study__Intercept, 0.975)),
  pr_or_lt_1 = c(mean(exp(ref_draws$mu) < 1), mean(exp(brms_draws$b_Intercept) < 1))
)

knitr::kable(
  compare_tbl |>
    dplyr::mutate(
      dplyr::across(where(is.numeric), ~ round(.x, 3))
    ),
  caption = "Cross-check of pooled effect and heterogeneity: bayesmeta vs brms+cmdstanr."
)
```

Cross-check caveat: `brms` cannot directly consume the exact Turner empirical heterogeneity prior as a simple built-in prior family, so this section uses an approximately aligned half-normal prior on the random-effect SD.

## Summary

This audit adds a transparent, uncertainty-aware extension to `Mortality EP.Rmd` by:

- making prior choices clinically interpretable on OR and log-OR scales,
- quantifying prior sensitivity,
- checking model fit with posterior predictive diagnostics,
- using calibrated probability language for conclusions, and
- optionally validating pooled inference through an independent `brms`/`cmdstanr` implementation.

## Session information

```{r}
sessionInfo()
```
