---
title: "Mortality"
author: "Omar Abdullah Gill"
date: "2026-04-10"
output: html_document
---
Loading of all packages
```{r}
pacman::p_load(bayesmeta,          # Bayesian Meta-Analysis
               BayesianPriorsTool, # Priors Building Tool
               dplyr,              # Data Wrangle
               tidyr,              # Data Wrangle
               meta,               # Forest Plot
               metafor,            # Effect Sizes
               ggdist,             # Distributions
               ggplot2,            # Plots
               patchwork,          # Plots
               here,
               readxl,             # Import data
               gt)  

# ggplot2 theme
theme_set(
  theme(
    plot.title.position = 'plot',
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(size = 14),
    panel.background = element_blank(),
    panel.grid.major.x = element_line(color = "gray80", linewidth = 0.3)
  )
)
```
Data

```{r}
# Consolidate all 6 studies 
mor_data <- data.frame(
  # Column 1: Study Names
  study = c("Vinther, 2021 (HBP)", "Wang, 2022 (LBAP)", 
            "Huang, 2022 (HBP)", "Pujol-Lopez, 2022 (LBAP)", 
            "Vijayaraman, 2023 (LBAP)", "PhysioSync-HF, 2026 (LBAP)"),
  
  # Group info for sorting/labeling (optional but good practice)
  subgroup = c("HBP", "LBAP", "HBP", "LBAP", "LBAP", "LBAP"),
  
  # Data columns: Events / Totals
  ai = c(0, 0, 1, 0, 2, 11),  # CSP Events
  n1 = c(25, 20, 25, 35, 50, 87), # CSP Totals
  ci = c(0, 0, 4, 2, 2, 4),    # BiVP Events
  n2 = c(25, 20, 25, 35, 50, 86) # BiVP Totals (Correction: BVP total is 86)
)




# View dataset
mor_data


mor_dat_OR <- escalc(
  measure = "OR",
  ai = ai, n1i = n1,
  ci = ci, n2i = n2,
  slab = study,
  data = mor_data
) |> 
  data.frame()

mor_dat_OR$sei <- sqrt(mor_dat_OR$vi)

# add subgroup back
mor_dat_OR$subgroup <- mor_data$subgroup

mor_dat_OR
```

Prior (vague)
```{r}
prior_mor_vague_mean_OR = 0
prior_mor_vague_sd_OR = 2.7

mu_dist_viz(mean = prior_mor_vague_mean_OR, 
            sd = prior_mor_vague_sd_OR,
            scale = "relative",
            xlabel = "Odds Ratio")
```

tau
```{r}
informative_mor_tau_prior_OR =
  TurnerEtAlPrior(outcome = "all-cause mortality",
                  comparator1 = "non-pharmacological",
                  comparator2 = "non-pharmacological")

informative_mor_prior_OR_mean = informative_mor_tau_prior_OR$parameters["tau", "mu"]

informative_mor_prior_OR_sd = informative_mor_tau_prior_OR$parameters["tau", "sigma"]


tau_dist_viz(dist = "log-normal",
             meanlog = informative_mor_prior_OR_mean,
             sdlog = informative_mor_prior_OR_sd)
```

Main_analysis
```{r,echo=FALSE}
mor_model =
  bayesmeta(y = mor_dat_OR$yi, 
            sigma = mor_dat_OR$sei, 
            labels = mor_dat_OR$study,
            # Priors
            mu.prior.mean = prior_mor_vague_mean_OR,   
            mu.prior.sd = prior_mor_vague_sd_OR,       
            tau.prior = informative_mor_tau_prior_OR$dprior 
  )
```
```{r}
posterior_mor_list = 
  list(
    mu_mean = mor_model$summary["mean", "mu"],
    mu_upper = mor_model$summary["95% upper", "mu"],
    mu_lower = mor_model$summary["95% lower", "mu"],
    
    tau_median = mor_model$summary["median","tau"],  
    tau_upper = mor_model$summary["95% upper","tau"],
    tau_lower = mor_model$summary["95% lower","tau"],
    
    theta_mean = mor_model$summary["mean", "theta"],
    theta_upper = mor_model$summary["95% upper", "theta"],
    theta_lower = mor_model$summary["95% lower", "theta"]
  )

## Forest plot 
forest_data_OR_mor = metabin(
  data = mor_dat_OR,
  studlab = study,
  
  event.e = ai,  # event.e = events in group 1
  n.e = n1,     # n.e = total in group 1
  event.c = ci,  # event.c = events in group 2
  n.c = n2,     # n.c = total in group 2
  
  sm = "OR",
  method.tau = "PM",
  
  # Very important: no frequentist analysis in this plot
  common = FALSE,
  random = FALSE
)

# Add Bayesian overall effect posterior summary
meta_forest_mor = metaadd(
  forest_data_OR_mor, # "prepared data" object
  type = "random",
  
  TE = posterior_mor_list$mu_mean,
  upper = posterior_mor_list$mu_upper,
  lower = posterior_mor_list$mu_lower
)  

# Add Bayesian Posterior Predictive Distribution summary
meta_forest_mor_predict = metaadd(
  meta_forest_mor, # object from above
  type = "prediction", # note that now is "prediction"
  
  TE = posterior_mor_list$theta_mean,
  upper = posterior_mor_list$theta_upper,
  lower = posterior_mor_list$theta_lower
)  

# Create a sentence to summarize tau posterior results
tau_OR = 
  paste0("\u03C4 = ", 
         round(posterior_mor_list$tau_median, 2),
         " [95% CrI ",
         round(posterior_mor_list$tau_lower, 2),
         ", ",
         round(posterior_mor_list$tau_upper, 2), "]")
```

Forest plot
```{r}
meta::forest(meta_forest_mor_predict,
             layout = "RevMan5",
             sortvar = TE,
             text.random = "Total (95% CrI)",
             text.predict = "95% Prediction Interval",
             text.addline1 = tau_OR,
             smlab = "Odds Ratio (log scale)",
             leftcols=c("studlab", "event.e", "n.e",
                        "event.c", "n.c", "effect.ci"),
             leftlabs=c("Study",  NA, NA, NA, NA, "OR"),
             
             pooled.events = TRUE,
             label.e = "CSP", 
             lab.c = "BVP",
             label.left = "Favors CSP",
             label.right = "Favors BVP",
             colgap = "5mm")
```



Probability plot
```{r, warning=FALSE, message=FALSE}
set.seed(123)

posterior_draws <- mor_model$rposterior(n = 10000, tau.sample = FALSE)

mu <- if (is.matrix(posterior_draws) || is.data.frame(posterior_draws)) {
  posterior_draws[, 1]
} else {
  posterior_draws
}

df <- data.frame(
  OR = exp(mu)
)

df <- df[is.finite(df$OR) & df$OR > 0, , drop = FALSE]


# 2. PROBABILITY OF BENEFIT
P_sup <- mean(df$OR < 1)


ci <- quantile(df$OR, probs = c(0.025, 0.975))

ci_df <- data.frame(
  xmin = ci[1],
  xmax = ci[2],
  y = 0
)

mean_or <- mean(df$OR)

mean_df <- data.frame(
  OR = mean_or,
  y = 0
)

#density bar
dens <- density(df$OR, adjust = 1.2)

dens_df <- data.frame(
  OR = dens$x,
  density = dens$y
)

p_density <- ggplot(dens_df, aes(x = OR, y = density)) +
  
  geom_area(fill = "grey85") +
  
  geom_area(
    data = subset(dens_df, OR <= 1),
    fill = "navy"
  ) +
  
  geom_vline(xintercept = 1, linetype = "dashed", linewidth = 1) +
  
 
# CREDIBLE INTERVAL BAR

geom_segment(
  data = ci_df,
  aes(x = xmin, xend = xmax, y = y, yend = y),
  linewidth = 1.5,
  color = "black"
) +
  
  # mean marker
  geom_point(
    data = mean_df,
    aes(x = OR, y = y),
    size = 3
  ) +
  
  scale_x_log10() +
  
  labs(
    x = "Odds Ratio (log scale)",
    y = "Density"
  ) +
  
  annotate(
    "text",
    x = ci[1],
    y = max(dens_df$density) * 0.75,
    label = paste0(round(P_sup * 100, 1), "%"),
    fontface = "bold",
    size = 4
  ) +
  
  theme_classic() +
  theme(
    panel.grid.major = element_line(color = "grey85"),
    panel.grid.minor = element_line(color = "grey92")
  )
```


```{r, warning=FALSE, message=FALSE}
#ECDF PLOT

ecdf_fun <- ecdf(df$OR)

x_vals <- exp(seq(
  log(min(df$OR)),
  log(max(df$OR)),
  length.out = 1000
))

cdf_df <- data.frame(
  OR = x_vals,
  cdf = ecdf_fun(x_vals)
)

p_cdf <- ggplot(cdf_df, aes(x = OR, y = cdf)) +
  
  geom_line(linewidth = 1) +
  
  geom_area(
    data = subset(cdf_df, OR <= 1),
    aes(y = cdf),
    fill = "navy"
  ) +
  
  geom_vline(xintercept = 1, linetype = "dashed", linewidth = 1) +
  
  scale_x_log10() +
  scale_y_continuous(limits = c(0, 1)) +
  
  labs(
    x = "Odds Ratio",
    y = "Cumulative Probability"
  ) +
  
  annotate(
    "text",
    x = 0.8,
    y = 0.65,
    label = paste0(round(P_sup * 100, 1), "%"),
    fontface = "bold",
    size = 4
  ) +
  
  theme_classic() +
  theme(
    panel.grid.major = element_line(color = "grey85"),
    panel.grid.minor = element_line(color = "grey92")
  )
p_density + p_cdf
```


Meta-regression Analysis with HF etiology

Data
```{r}
# Creating the final analysis dataframe
analysis_df <- data.frame(
  study = c("Vinther", "Wang", "Pujol-Lopez", "Vijayaraman", "PhysioSync-HF"),
  # yi = Log Odds Ratio, sei = Standard Error from your previous analysis
  yi  = c(0.000, 0.000, -1.667, 0.000, 1.087), 
  sei = c(2.019, 2.024, 1.567, 1.020, 0.605),
  # Using the ischemic_pct we just calculated
  ischemic_pct = c(22.0, 0.0, 31.4, 39.0, 12.7)
)

# Creating the design matrix
# This allows the model to estimate the Intercept (alpha) and the Slope (beta)
X_matrix <- model.matrix(~ ischemic_pct, data = analysis_df)
```

Mian Model for regression (HF)
```{r}
# Running the model
meta_reg_model <- bmr(
  y      = analysis_df$yi,
  sigma  = analysis_df$sei,
  X      = X_matrix,
  labels = analysis_df$study,
  
  # Bayesian Priors
  beta.prior.mean = c(0, 0),
  beta.prior.sd   = c(0.82, 1.5),
  tau.prior       = function(x) dhalfnormal(x, scale = 0.5)
)

# View the summary output
summary(meta_reg_model)


# Extract posterior samples
set.seed(123)
post_samples <- meta_reg_model$rposterior(n = 1000) |> data.frame()

# Probability that increasing Ischemic % favors CSP (Slope < 0)
prob_csp_favors_ischemic = mean(post_samples$ischemic_pct < 0) * 100

cat("Probability that Etiology favors CSP as Ischemic % increases:", round(prob_csp_favors_ischemic, 1), "%")

# Proportion of the posterior that is negative
mean(post_samples$ischemic_pct < 0)
```



Bayesian random-effects meta-regression demonstrated a negative association between ischemic patient proportion and log odds ratio for mortality (posterior mean β = −0.015, 95% CrI −0.078 to 0.049), suggesting that increasing ischemic burden may shift the mortality benefit toward conduction system pacing (CSP). Clinically, this corresponds to an approximate 14% greater mortality benefit toward CSP for every 10% increase in ischemic patients. However, the 95% credible interval crossed the null, indicating that the evidence remains suggestive rather than conclusive,likely due to the small number of included studies.  The intercept suggested that in predominantly non-ischemic cohorts, outcomes may numerically favor biventricular pacing, supporting the hypothesis that BVP may  be relatively more effective in non-ischemic cardiomyopathy, whereas CSP may confer greater benefit in ischemic populations.


```{r}
set.seed(123)

# posterior draws
post_samples <- meta_reg_model$rposterior(n = 10000, tau.sample = FALSE) |>
  data.frame()

# ALPHA (Intercept) = effect when ischemic_pct = 0
alpha_draws <- post_samples$X.Intercept.

# Probability that BVP is favored in purely non-ischemic patients
# OR > 1 = favors BVP
prob_alpha_BVP <- mean(exp(alpha_draws) > 1) * 100

# Probability that CSP is favored in purely non-ischemic patients
prob_alpha_CSP <- mean(exp(alpha_draws) < 1) * 100

cat(
  "Probability BVP is favored in purely non-ischemic patients:",
  round(prob_alpha_BVP, 1), "%\n"
)

cat(
  "Probability CSP is favored in purely non-ischemic patients:",
  round(prob_alpha_CSP, 1), "%\n"
)


# BETA (Slope) = change with increasing ischemic %
beta_draws <- post_samples$ischemic_pct

# Main hypothesis: more ischemic patients -> CSP benefit increases
prob_beta_CSP <- mean(beta_draws < 0) * 100

# Opposite direction
prob_beta_BVP <- mean(beta_draws > 0) * 100

cat(
  "Probability increasing ischemic burden favors CSP:",
  round(prob_beta_CSP, 1), "%\n"
)

cat(
  "Probability increasing ischemic burden favors BVP:",
  round(prob_beta_BVP, 1), "%\n"
)


# CLINICALLY MEANINGFUL EFFECT PER 10% INCREASE
OR_10pct <- exp(beta_draws * 10)

prob_10pct_CSP <- mean(OR_10pct < 1) * 100

cat(
  "Probability each 10% ischemic increase improves mortality toward CSP:",
  round(prob_10pct_CSP, 1), "%\n"

)
```

Table
```{r}
# CREATE PUBLICATION-READY GT TABLE

probability_table <- tibble(
  Parameter = c(
    "Intercept (α): BVP favored at 0% ischemic",
    "Intercept (α): CSP favored at 0% ischemic",
    "Slope (β): Increasing ischemic burden favors CSP",
    "Slope (β): Increasing ischemic burden favors BVP",
    "Clinical effect: Every 10% ischemic increase favors CSP"
  ),
  
  `Posterior Probability (%)` = c(
    round(prob_alpha_BVP, 1),
    round(prob_alpha_CSP, 1),
    round(prob_beta_CSP, 1),
    round(prob_beta_BVP, 1),
    round(prob_10pct_CSP, 1)
  ),
  
  `Clinical Interpretation` = c(
    "Probability BVP is superior in purely non-ischemic patients",
    "Probability CSP is superior in purely non-ischemic patients",
    "Probability ischemic substrate progressively shifts benefit toward CSP",
    "Probability ischemic substrate progressively shifts benefit toward BVP",
    "Probability every 10% rise in ischemic burden improves mortality toward CSP"
  )
)


# GT TABLE
probability_table |>
  gt() |>
  tab_header(
    title = md("**Bayesian Meta-Regression: Posterior Probability Summary**"),
    subtitle = "Clinical interpretation of intercept and etiology slope"
  ) |>
  cols_align(
    align = "center",
    columns = `Posterior Probability (%)`
  ) |>
  cols_width(
    Parameter ~ px(350),
    `Posterior Probability (%)` ~ px(180),
    `Clinical Interpretation` ~ px(500)
  ) |>
  fmt_number(
    columns = `Posterior Probability (%)`,
    decimals = 1
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) |>
  tab_options(
    table.width = pct(100),
    heading.title.font.size = px(18),
    heading.subtitle.font.size = px(13)
  )



```

Plot

```{r}

# 1. Data
plot_df <- analysis_df

# 2. Posterior regression line
set.seed(123)
post <- meta_reg_model$rposterior(n = 5000, tau.sample = FALSE) |> 
  data.frame()

# Create smooth prediction grid
x_grid <- seq(min(plot_df$ischemic_pct),
              max(plot_df$ischemic_pct),
              length.out = 200)

pred_mat <- sapply(x_grid, function(x) {
  post$X.Intercept. + post$ischemic_pct * x
})

pred_df <- data.frame(
  ischemic_pct = x_grid,
  mean = apply(pred_mat, 2, mean),
  lower = apply(pred_mat, 2, quantile, 0.025),
  upper = apply(pred_mat, 2, quantile, 0.975)
)

# 3. Plot
ggplot() +
  
  # Credible interval band
  geom_ribbon(
    data = pred_df,
    aes(x = ischemic_pct, ymin = lower, ymax = upper),
    fill = "skyblue",
    alpha = 0.3
  ) +
  
  # Posterior mean line
  geom_line(
    data = pred_df,
    aes(x = ischemic_pct, y = mean),
    linewidth = 1.2,
    color = "blue"
  ) +
  
  # Study points
  geom_point(
    data = plot_df,
    aes(x = ischemic_pct, y = yi),
    size = 3
  ) +
  
  # Study labels (ANCHORS)
  geom_text(
    data = plot_df,
    aes(x = ischemic_pct, y = yi, label = study),
    vjust = -1,
    size = 3
  ) +
  
  # Reference line (no effect)
  geom_hline(yintercept = 0, linetype = "dashed") +
  
  labs(
    x = "Ischemic Burden (%)",
    y = "Log Odds Ratio (CSP vs BVP)",
    title = "Bayesian Meta-Regression: Effect Modification by Ischemic Burden"
  ) +
  
  theme_classic()


```

